\section{Issue 14}
\paragraph{
The video camera provides such an accurate and convincing record of contemporary life that it has become a more important form of documentation than written records.
}
\subsection{Score 6}


According to the speaker, the video recording is a more important means of document hag contemporary life than a written record because video recordings are more accurate and convincing.
Although I agree that a video provides a more objective and accurate record of an event's spatial aspects, there is far more to document ha life than what we see and hear.
Thus the speaker overstates the comparative significance of video as a documentary tool.


For the purpose of documenting temporal, spatial events and experiences, I agree that a video record is usually more accurate and more convincing than a written record.
It is impossible for anyone, no matter how keen an observer and skilled a journalist, to recount ha complete and objective detail such events as the winning touchdown at the Super Bowl, a.


Ballanchine ballet, the Tournament of Roses Parade, or the scene at the intersection of.


Florence and Normandy streets during the 1992 Los Angeles riots.
Yet these are important events in contemporary life the sort of events we might put ha a time capsule for the purpose of capturing our life and times at the turn of this millennium.


The growing documentary role of video is not limited to seminal events like those described above.
Video surveillance cameras are objective witnesses with perfect memories.
Thus they can play a vital evidentiary role in legal proceedings--such as those involving robbery, drug trafficking, police misconduct, motor vehicle violations, and even malpractice in a hospital operating room.
Indeed, whenever moving images are central to an event the video camera is superior to the written word.
A written description of a hurricane, tornado, or volcanic eruption cannot convey its immediate power and awesome nature like a video record.
A diary entry cannot "replay" that wedding reception, dance recital, or surprise birthday party as accurately or objectively as a video record.
And a real estate brochure cannot inform about the lighting, spaciousness, or general ambiance of a featured property nearly as effectively as a video.


Nonetheless, for certain other purposes written records are advantageous to and more appropriate than video records.
For example, certain legal matters are best left to written documentation: video is of no practical use ha documenting the terms of a complex contractual agreement, an incorporation, or the establishment of a trust.
And video is of little use when it comes to documenting a person's subjective state of mind, impressions, or reflections of an event or experience.
Indeed, to the extent that personal interpretation adds dimension and richness to the record, written documentation is actually more important than video.


Finally, a video record is of no use in documenting statistical or other quantitative information.


Returning to the riot example mentioned earlier, imagine relying on a video to document the financial loss to store owners, the number of police and firefighters involved, and so forth.


Complete and accurate video documentation of such information would require video cameras at every street corner and in every aisle of every store.


In sum, the speaker's claim overstates the importance of video records, at least to some extent.
When it comes to capturing, storing, and recalling temporal, spatial events, video records are inherently more objective, accurate, and complete.
However, what we view through a camera lens provides only one dimension of our life and times; written documentation will always be needed to quantify, demystify, and provide meaning to the world around us.
